### 2022-03-21 chapters/04-chapter-4.tex
txs auto checkin

>>>>

\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}

	\caption{Algoritme pengambilan data \textit{real-time}}\label{alg:realtime-ret}
\end{algorithm}

\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}

	\caption{Algoritme \textit{correlation analysis}}\label{alg:corr-analysis}
\end{algorithm}

\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}

	\caption{Algoritme \textit{critical path analysis}}\label{alg:crit-analysis}
\end{algorithm}

\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}

	\caption{Algoritme \textit{critical path analysis}}\label{alg:corr-analysis}
\end{algorithm}
